### 2014-03-11 src/methodology.Rnw
update
udpate

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false* \\
\hline
\end{tabular}
\caption{PIT Mutation Opeators}
\label{tbl:pitop}
\end{table}

@@

\subsection{Mutant Clustering}
For mutant clustering, we were unable to directly apply clustering based on distinct mutants as suggested by Hussain~\cite{hussain2008mutation}. However, we were able to apply clustering techniques on mutation operators, thus turning it to a set of selected operators.

>>>>

\begin{table}[h]\footnotesize
\begin{tabular}{ll}
\hline \hline \\
\pitic & Invert negatives \\
\pitrv & Change return values \\
\pitm & Modify arithmetic operators\\
\pitvmc & Remove void method calls \\
\pitnc & Negate conditional statements \\
\pitcb & Modify boundary conditions \\
\piti & Modify increment/decrement \\
\pitnvmc & Replace non-void method calls \\
\pitcc & Replace constructor calls \\
\pitic & Replace inline constants \\
\piti & Remove increment/decrement \\
\pitemv & Replace member variable assignments \\
\pites & Modify switch statements \\
\pitrs & Remove switch elements* \\
\pitrc & Make conditionals true \\
\pitnc & Make conditionas false* \\
\hline
\end{tabular}
\caption{PIT Mutation Opeators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

@@
